---
title: "Data 607 Assignment 03"
author: "Md. Tanzil Ehsan"
date: "02/16/2025"
output: openintro::lab_report
editor_options: 
  chunk_output_type: inline
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(lubridate)
```

##Loading data from website


```{r }
raw_file = 
  'https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv'
```
## Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset ##[https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either “DATA” or “STATISTICS”

```{r pressure, echo=FALSE}
majors <-as_tibble(read.csv(raw_file))
majors_sub <- majors %>% 
    mutate(matched_name = str_match(Major,'.*DATA.*|.*STATISTICS.*')) %>%
    select(Major,matched_name) %>%
    filter(!is.na(matched_name))
majors_sub
```
##Write code that transforms the data below:
#create the vector of the DATA
```{r}
fruits <- c("bell pepper","bilberry", "blackberry","blood orange","blueberry","
            cantaloupe", "chili pepper", "cloudberry",  "elderberry", "lime",
            "lychee" , "mulberry" , "olive", "salal berry")
fruits
```


```{r}
fruits <- c("bell pepper","bilberry", "blackberry","blood orange","blueberry",
            "cantaloupe", "chili pepper", "cloudberry",  "elderberry", "lime", 
            "lychee" , "mulberry" , "olive", "salal berry")

```


```{r}
cat(paste0("c(",paste0(sep = '"',fruits, collapse = ', ', sep='"'),paste(")")))
```
#3 Describe, in words, what these expressions will match:

(.)\1\1
“(.)(.)\\2\\1”
(..)\1
“(.).\\1.\\1”
“(.)(.)(.).*\\3\\2\\1”


##Answer:

(.)\1\1 - Any two characters that repeats in the reverse order.
“(.)(.)\\2\\1” - Any two characters that repeats in the same order.
“(.).\1.\1” - Any single character that repeats two more times, with each repetition after another single variable character.
“(.)(.)(.).*\3\2\1” - Any three characters that repeat in the reverse order after any number of variable characters.

#4 Construct regular expressions to match words that: Start and end with the same character. Contain a repeated pair of letters (e.g. “church” contains “ch” repeated twice.) Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.)


##A_regex_expr1_Start and end with the same character

```{r}
df.names <-c("anna", "church", "bob", "harry","paul", "eleven", "bubble")
regex_expr1 ="^(.)((.*\\1$)|\\1?$)"
str_subset(df.names,regex_expr1)
```
##B_regex_expr2_Contain a repeated pair of letters
```{r}
regex_expr2 = "([A-Za-z][A-Za-z]).*\\1"
str_subset(df.names,regex_expr2)
```

##C_regex_expr3_Contain one letter repeated in at least three places

```{r}
regex_expr3 = "([A-Za-z]).*\\1.*\\1"
str_subset(df.names,regex_expr3 )
```
